Insert the article title here

### 2020-07-24 tex/background.tex
fix typo
typo

In the last years polar dielectrics, like Silicon Carbide (SiC), have caught the attention as an alternative to plasmonic metals, due to their low optical losses in in the
mid to long wave infrared. Nanostructures of these materials show figure of merits that exceed that are not possible using plasmonic metals. This effect is due to the properties 
of the dielectric in the mid/long infrared region, where the real part has a negative value and the imaginary part is very small. This dielectric behavior is similar to the one 
be observed in metals like silver in the blue part of the wavelength spectrum. 
In plasmonics, when we illuminate a small particle made of metallic materials we will observe that certain wavelengths will excite a surface plasmon, which is the result of 
the oscillation of free electrons. The main difference with polar dielectrics like SiC is that for this material, is that the frequency of the incoming light matches instead the
resonance frequency of the Si and C sublattices \cite{caldwell2015,rockstuhl2005}. This excitation leads to a strong extinction cross section at the resonance wavelength, and an 
enhanced near field amplitude. These behavior can be model  with the same approached used for Localized surface plasmon resonance, and when the wavelength is bigger than the size
of the nanoparticle, we can still applied the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.

When studying both Phonon Polaritons and Plasmons resonances, we can analyze the spectrums by measuring different quantities. We can measure scattering cross section, extinction cross section 
(scattering plus absorption), as well as reflection. These different approaches are comparable since the \textit{variable of interest} is the wavelength/frequency at which 
the resonance modes happen. Whether we measure reflection or extinction cross section, the wavelength/frequency at which the peaks happen remains the same. Along the course of this 
work we will concentrate on study the wavelength/frequency at which the resonance modes happen and we will aim to replicate results from Rockstuhl et al. 2005 \cite{rockstuhl2005} and 
from Ellis et al. 2016 \cite{ellis2016}, and we will validate our software against experimental results from Ellis et al. 2016 \cite{ellis2016}.

>>>>

In the last years polar dielectrics, like Silicon Carbide (SiC), have caught the attention as an alternative to plasmonic metals, due to their low optical losses in in the
mid to long wave infrared. Nanostructures of these materials show figure of merits that are not possible using plasmonic metals. This effect is due to the properties 
of the dielectric in the mid/long infrared region, where the real part has a negative value and the imaginary part is very small. This dielectric behavior is similar to the one 
be observed in metals like silver in the blue part of the wavelength spectrum. 
In plasmonics, when we illuminate a small particle made of metallic materials we will observe that certain wavelengths will excite a surface plasmon, which is the result of 
the oscillation of free electrons. The main difference with polar dielectrics like SiC is that for this material, is that the frequency of the incoming light matches instead the
resonance frequency of the Si and C sublattices \cite{caldwell2015,rockstuhl2005}. This excitation leads to a strong extinction cross section at the resonance wavelength, and an 
enhanced near field amplitude. These behavior can be model  with the same approached used for Localized surface plasmon resonance, and when the wavelength is bigger than the size
of the nanoparticle, we can still applied the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.

When studying both Surface Phonon Polaritons and Surface Plasmons resonances, we can analyze the spectrums by measuring different quantities. We can measure scattering cross section, extinction cross section 
(scattering plus absorption), as well as reflection. These different approaches are comparable since the \textit{variable of interest} is the wavelength/frequency at which 
the resonance modes happen. Whether we measure reflection or extinction cross section, the wavelength/frequency at which the peaks happen remains the same. Along the course of this 
work we will concentrate on study the wavelength/frequency at which the resonance modes happen and we will aim to replicate results from Rockstuhl et al. 2005 \cite{rockstuhl2005} and 
from Ellis et al. 2016 \cite{ellis2016}, and we will validate our software against experimental results from Ellis et al. 2016 \cite{ellis2016}.
